Twists of supersymmetric gauge theories

### 2020-01-14 paper.tex
minor edits

\item An (elliptic) action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$  \brian{this seems to fail for all our examples.}.
\end{itemize}
These are required to satisfy the following conditions:
\begin{itemize}
\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, differential $Q$ and the interaction term $I$.

@@

@@

\subsection{$\cN=1$ with chiral multiplet matter} 
There is a minimal supersymmetric field theory with $\cN=1$ supersymmetry consisting of a pure gauge theory coupled to supersymmetric matter depending on a complex representation $R$.

@@

We consider $\cN=(0,2)$ super Yang-Mills coupled to the $\cN=(0,2)$ chiral multiplet with values in a representation $R$. 
\brian{Should we also compute what happens to the $(0,2)$ Fermi multiplet?}

@@

>>>>

\item An (elliptic) action $I_\fg$ of its super Lie algebra $\fg$ with $I^{(k)}_\fg = 0$ for $k\geq 2$ 
\end{itemize}
These are required to satisfy the following conditions:
\begin{itemize}
\item The $G$-action on $\cE$ preserves the symplectic pairing $\omega$, differential $Q$ and the interaction term $I$.

@@

\brian{How do we see the various flavors of matter multiplets? For instance, in $2d (0,2)$ there is the Fermi multiplet and the chiral multiplet. 
Your description only sees the chiral.
In $2d (0,4)$ there are even more: the hypermultiplet (two $(0,2)$ chirals), the twisted hypermultiplet (the same as the hyper, different $R$-symmetry), the fermi multiplet (two $(0,2)$ fermi multiplets). 
I'm not sure which your description sees, but I have a hunch it's the $(0,4)$ hypermultiplet. 
What is the reason for only seeing certain multiplets via this general setup?
}

@@

\subsection{$\cN=1$ with chiral multiplet matter} 
We consider $\cN=1$ supersymmetric Yang-Mills for a Lie algebra $\fg$ coupled to supersymmetric matter.
The matter consists of the $\cN=1$ chiral multiplet valued in a complex representation $R$.

@@

We consider $\cN=(0,2)$ super Yang-Mills for a Lie algebra $\fg$ coupled to $\cN=(0,2)$ supersymmetric matter. 
The supersymmetric matter consists of the $\cN = (0,2)$ chiral multiplet with values in a representation $R$.

\brian{Should we also compute what happens to the $(0,2)$ Fermi multiplet?}

@@

\brian{Confused.}
